---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fkcentroids

<!-- badges: start -->
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/fkcentroids)](https://CRAN.R-project.org/package=fkcentroids) [![CRAN_Downloads](https://cranlogs.r-pkg.org/badges/grand-total/fkcentroids)](https://CRAN.R-project.org/package=fkcentroids)
<!-- badges: end -->

Functional K-Centroids Clustering Using Phase and Amplitude Components

## What is fkcentroids?

...

## How can I get fkcentroids?

<!-- Version 0.4.0 of this package is available on [CRAN](https://cran.r-project.org/package=fkcentroids): -->

<!-- ``` r -->
<!-- install.packages("fkcentroids") -->
<!-- library(fkcentroids) -->
<!-- ``` -->

You can install the development version (version 0.0.0.9000) of `fkcentroids` via:

``` r
devtools::install_github("seungwoo-stat/fkcentroids")
library(fkcentroids)
```

## How do I use it?

...

```{r example}
library(fkcentroids)
# examples
```

...

Refer to the package documentation for an overview of the support range for each function.

``` r
?`fkcentroids-package`
```

Moreover, one dataset ...

## Where can I learn more?

Visit [this repo](https://github.com/seungwoo-stat/fkcentroids-paper) for code to reproduce the figures and analysis from the paper Kang and Oh (2026).

## References

Seungwoo Kang and Hee-Seok Oh. Multiview Representation and Clustering of Functional Data. *Unpublished Manuscript*, 2026.
