---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
set.seed(0)
```

# fkcentroids

<!-- badges: start -->
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/fkcentroids)](https://CRAN.R-project.org/package=fkcentroids) [![CRAN_Downloads](https://cranlogs.r-pkg.org/badges/grand-total/fkcentroids)](https://CRAN.R-project.org/package=fkcentroids)
<!-- badges: end -->

Functional K-Centroids Clustering Using Phase and Amplitude Components

## What is fkcentroids?

`fkcentroids` aims to conduct functional *k*-means and *k*-medians clustering by jointly considering the phase and amplitude variations of functions. The routines first synchronizes each function, thereby separating phase and amplitude components. For the phase components, a Bayes Hilbert space structure is imposed to enable effective analysis, while for the amplitude components, the usual *L*<sup>2</sup> geometry is employed. By weighting phase and amplitude variation differently, clustering results can be obtained from multiple perspectives. Routines for function synchronization, as well as clustering procedures based on the extracted phase and amplitude components,
are provided.

## How can I get fkcentroids?

<!-- Version 0.4.0 of this package is available on [CRAN](https://cran.r-project.org/package=fkcentroids): -->

<!-- ``` r -->
<!-- install.packages("fkcentroids") -->
<!-- library(fkcentroids) -->
<!-- ``` -->

You can install the development version (version 0.0.0.9003) of `fkcentroids` via:

``` r
devtools::install_github("seungwoo-stat/fkcentroids")
library(fkcentroids)
```

## How do I use it?

Using the Berkeley growth curves from the **fda** package, the functions can be clustered using `fkmeans()` (or `fkmedians()`) after decomposing them into their phase and amplitude components. Weights between phase and amplitude variations can be controlled by the argument `alpha_scale`, which is set to 1 by default.

```{r example}
library(fkcentroids) 
data(growth, package = "fda")
Ytilde <- cbind(growth$hgtm, growth$hgtf)
x <- growth$age
(res_pa <- fkmeans(Ytilde, x, t = seq(0, 1, length.out = 100),
                   sync_map = "auc", sync_args = 1, alpha_scale = 1, 
                   k = 2, nstart = 10))
(res_raw <- fkmeans(Ytilde, x, t = seq(0, 1, length.out = 100),
                    sync_map = "none", k = 2, nstart = 10))
```
It can be checked that the correct classification rate using phase and amplitude components of each curve is `r round(93 - mclust::classError(res_pa$cluster, c(rep(1,39),rep(2,54)))$errorRate * 93)`/93, whereas functional *k*-means clustering conducted directly on the observed curves yields correct classification rate of `r round(93 - mclust::classError(res_raw$cluster, c(rep(1,39),rep(2,54)))$errorRate * 93)`/93.
Refer to the package documentation for details.

``` r
?`fkcentroids-package`
```

## Where can I learn more?

Visit [this repo](https://github.com/seungwoo-stat/fkcentroids-paper) for code to reproduce the figures and analysis from the paper Kang and Oh (2026).

## References

Seungwoo Kang and Hee-Seok Oh. Multiview Functional Clustering Using Latent Representations of Phase and Amplitude Components. *Unpublished Manuscript*, 2026.
